rotation_runs2019

### 2019-12-10 inst/documents/rotation_runs2019.Rmd
cumulativ mortality recording, correcting gens_under_thresh for mortality

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'

@@

    # summarise results per scenario
    # note this is also currently calc at end of run_rot() here is probably better
    gens <- gens_under_thresh(dfres)

    # to be able to save as for rot or seq
    if ( linputs$rot_interval == 0 ) {gens_seq <- as.numeric(gens)}
    else                             {gens_rot <- as.numeric(gens)}

@@

  # add scenario id column and difference onto results
  # df_in_out is one row
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, id=i))
  df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

>>>>

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'

@@

    # summarise results per scenario
    # this calcs for whole run, at end of run_rot() it calcs per insecticide
    if ( linputs$mort_or_freq == 'freq' ) threshold <- linputs$freq_thresh
    else if ( linputs$mort_or_freq == 'mort' ) threshold <- linputs$mort_thresh

    #gens <- gens_under_thresh(dfres=dfres, threshold=threshold, mort_or_freq=linputs$mort_or_freq)

    # 10/12/19 change to recording end generations and mean mortality
    gens <- calc_max_gens(dfres=dfres)
    cum_mort <- cumulat_mortality(dfres=dfres)

    # to be able to save as for rot or seq
    if ( linputs$rot_interval == 0 ) {gens_seq <- as.numeric(gens)
                                      mort_seq <- cum_mort/gens_seq}
    else                             {gens_rot <- as.numeric(gens)
                                      mort_rot <- cum_mort/gens_rot}

@@

  # add scenario id column and difference onto results
  # df_in_out is one row
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, mort_rot=mort_rot, mort_seq=mort_seq, id=i))

  df_in_out$gens_rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

  df_in_out$mort_rot_minus_seq <- df_in_out$mort_rot - df_in_out$mort_seq

### 2019-12-10 inst/documents/rotations_notes.Rmd
cumulativ mortality recording, correcting gens_under_thresh for mortality

>>>>

# 9/12/19

Thinking that I can output mean % mortality over all generations and that will give us a better comparison between sequences and rotations (alongside going back to recording total generations untill all insecticides exhausted).

# 10/12/19

corrected recordning of gens_under_thresh for mortality even though probably not going to use anymore

~ set recording of 
i  total generations (maybe from run_rot)
ii cumulative or mean mortality (maybe post-processed)

I think better to use mean mortality because it is more obviously meaningfull, and a potential way of comaparing runs even id they have different lengths or number of insecticides.
